The `forestecology` R package for modeling interspecies competition between trees

### 2021-02-15 etc/paper/forestecology.Rmd
Replicated PLOS One simulations

1. Compute the growth of trees based on census data
1. Add spatial information:
    1. Define buffer region trees.
    1. Add spatial cross-validation block information.
1. Compute focal versus competitor tree information.
1. Fit model and make predictions.
1. Additionally: Evaluate model performance using spatial cross-validation.
1. Additionally: Evaluate the effect of competitor species identity using permutation tests.

@@

@@

## Visualize posterior distributions {#viz-posterior-distributions}

>>>>

1. Compute the growth of trees based on census data
1. Add spatial information:
    1. Define buffer region trees.
    1. Add spatial cross-validation block information.
1. Compute focal versus competitor tree information.
1. Fit model and make predictions.
1. Visualize model results.
1. Additionally: Evaluate model performance using spatial cross-validation.
1. Additionally: Evaluate the effect of competitor species identity using permutation tests.

@@

The next step in the our analysis sequence is to add additional spatial information to our main data frame: defining a buffer region of trees as well as adding spatial cross-validation block information.

@@

## Visualize model results {#viz-posterior-distributions}
